AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-10-19 Paper/main.tex
10-19 paper

In Table~\ref{Tab:02}, we list the performance of methods in spatial or temporal domain and the stacking of methods. 
Temporal AttCRISPR, TAC for short, achieved Spearman correlation coefficients of 0.857, 0.844, 0.851 in above three dataset. 
Spatial AttCRISPR, SpAC for short, corresponds to 0.862, 0.854, 0.857. In the absence of hand-crafted biological features. 
Ensemble AttCRISPR achieve the best performance of our knowledge, corresponds to 0.868, 0.859, 0.862. 
\begin{table}[!tpb]
    \processtable{wait2write\label{Tab:02}} 
    {\begin{tabular}{@{}llll@{}}\toprule
        Method & WT-SpCas9 & eSpCas9(1.1) & SpCas9-HF1\\\midrule
        XGBoost & 0.845 & 0.831 & 0.818\\
        MLP & 0.842 & 0.846 & 0.844\\
        CNN & 0.846 & 0.831 & 0.834\\
        RNN & 0.856 & 0.849 & 0.851\\
        TAC & 0.857 & 0.844 & 0.851\\
        SpAC & 0.862 & 0.854 & 0.857\\
        \textbf{EnAC} & \textbf{0.868} & \textbf{0.859} & \textbf{0.862}\\
        CRISPRpred(SEQ) & 0.838 & 0.830 & 0.821\\
        \botrule
    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: wait2write}
\end{table}

>>>>

In Table~\ref{Tab:02}, we list the performance of methods in spatial or temporal domain and the stacking of methods. 
Temporal AttCRISPR, TAC for short, achieved Spearman correlation coefficients of 0.857, 0.844, 0.851 in above three dataset. 
Spatial AttCRISPR, SpAC for short, corresponds to 0.862, 0.854, 0.857. In the absence of hand-crafted biological features. 
Ensemble AttCRISPR achieve the best performance of our knowledge, corresponds to 0.868, 0.859, 0.862.

In addition, in Table~\ref{Tab:02}, the performance of other methods without using hand-crafted biological features, are also recorded. 
Regardless of the method we developed, RNN reported by \citeauthor{wang2019optimized}, which can be categorized as the method in temporal domain, 
is the most predictive with Spearman correlation coefficients of 0.856, 0.849, 0.851. 
It's obvious that the ensemble AttCRISPR is better at prediction (Figure~6\vphantom{\ref{fig:06}}a-c). 
Furthermore, the prediction ability of models could be boosted by addition of other hand-crafted biological features, which can't be obtained directly by sequence information.

Hence, the second experiment is designed to compare the performance of standard AttCRISPR (hand-crafted biological features are used to improve performance of ensemble AttCRISPR)
 and current state-of-the-art method, DeepHF (the RNN mentioned above integrated with hand-crafted biological features).
\begin{table}[!tpb]
    \processtable{wait2write\label{Tab:02}} 
    {\begin{tabular}{@{}llll@{}}\toprule
        Method & WT-SpCas9 & eSpCas9(1.1) & SpCas9-HF1\\\midrule
        XGBoost & 0.845 & 0.831 & 0.818\\
        MLP & 0.842 & 0.846 & 0.844\\
        CNN & 0.846 & 0.831 & 0.834\\
        RNN & 0.856 & 0.849 & 0.851\\
        TAC & 0.857 & 0.844 & 0.851\\
        SpAC & 0.862 & 0.854 & 0.857\\
        \textbf{EnAC} & \textbf{0.868} & \textbf{0.859} & \textbf{0.862}\\
        CRISPRpred(SEQ) & 0.838 & 0.830 & 0.821\\
        \botrule
    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: wait2write}
\end{table}
